---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Chidozie Chukwumba"
output:
   rmarkdown::html_document:
    theme: cerulean
    highlight: breezedark
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

### *I chose this dataset because I wish to learn how plastics are adversely affecting the environment and what measures are being taken combat this issue. This dataset will help me understand the different types of plastics and what I, as an individual, can do to assist in this noble cause.* *[plastics dataset](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-26/readme.md)*

```{r read-examine-data}
plastics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-26/plastics.csv')
dplyr::glimpse(plastics)
```

<br><br>

## Question 1

#### Which two parent companies produce the most plastics in Argentina?

### Methods
```{r United_States_plastics}

plastics %>%
  filter(country == "Argentina") %>%
  slice(1:10) %>%
   ggplot(aes(x = grand_total,
              y = parent_company)) +
  geom_col(color = "grey0",
           fill = "cyan") +
  theme_classic() +
  labs(x = "Total (plastics)",
       y = "Parent Company")
 
```


### Answer

**Unbranded and Grand Total**


<br><br>

## Question 2

#### Does The Coca-Cola Company produce more plastics than PepsiCo in the United States?

### Methods
```{r United_States_parent_company}
plastics %>%
  filter(country == "United States of America") %>%
  slice(1:10) %>%
  distinct() %>%
   ggplot(aes(x = grand_total,
              y = parent_company)) +
  geom_col(color = "red2",
           fill = "dodgerblue2") + 
  labs(x = "Total (plastics)",
       y = "Parent Company") + 
  theme_classic() 

```


### Answer

**No, they do not.**

<br><br>

## Question 3

#### Which parent company produced the most plastics in the China?


### Methods
```{r China_plastics}

plastics %>%
  filter(country == "China") %>%
  slice(1:10) %>%
  distinct() %>%
   ggplot(aes(x = grand_total,
              y = parent_company)) +
  geom_col(color = "gold",
           fill = "firebrick2") +
  theme_classic() +
  labs(x = "Total (plastics)",
       y = "Parent Company")
       

  
```

### Answer

**Grand Total**


<br><br>

## Question 4

#### Does the parent company, Grand Total, produce the most plastics in India?

### Methods
```{r India_plastics}

plastics %>%
  filter(country == "India") %>%
  slice(1:10) %>%
   ggplot(aes(x = grand_total,
              y = parent_company)) +
  geom_col(color = "goldenrod2",
           fill = "chartreuse2") +
  theme_classic() +
  labs(x = "Total (plastics)",
       y = "Parent Company") 
  
```


### Answer

**Yes**
